PANCHANGE_data_preprocessing

### 2020-07-23 PANCHANGE_data_preprocessing2020-07-15.Rmd
created phq missingness chunks

********************** 
++KT LEFT OFF HERE
**********************

@@

#Missigness of questionnaire items
+++CH: We need to discuss how we want to exclude these participants that are missing answers to the questionnaires
```{r missingness}

```{r Exclusion of participants because of missing questionnaire items}
#dim(dat.no.sex.no.age.no.ibd)
#dat.no.sex.no.age.no.ibd.incomplete.questionnaire <- dat.no.sex.no.age.no.ibd %>%
#  filter(#ADD CONDITION HERE)
#dim(dat.no.sex.no.age.no.ibd.incomplete.questionnaire)
#
#dim(dat.no.sex.no.age.no.ibd)[1]-dim(dat.no.sex.no.age.no.ibd.incomplete.questionnaire)[1]

@@

skimr::skim(dat.glad)
```
The complete rate for sex, gender and age should be 1 now.

>>>>

@@

#Missigness of questionnaire items
+++CH: We need to discuss how we want to exclude these participants that are missing answers to the questionnaires

Complete case data for PHQ, GAD and PCL - 3345 remaining, drop 35,036.
```{r complete cases only}
all.items <- c(phq.items_prepan,
                phq.items_base,
                phq.items_retro,
                gad.items_prepan,
                gad.items_base,
                gad.items_retro,
                pcl.items_prepan,
                pcl.items_base,
                pcl.items_retro)

dat.no.sex.no.gender.no.age.no.ibd.complete.cases <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, all.items ]),]

dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases)
dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases)[1]
```
Missingness for PHQ
```{r phq missingness baseline}
dat.no.sex.no.gender.no.age.no.ibd.phq.base <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na.per.person.phq =
      rowSums(is.na(dat.no.sex.no.gender.no.age.no.ibd[,colnames(dat.no.sex.no.gender.no.age.no.ibd) %in% phq.items_base]))
  )

freq(dat.no.sex.no.gender.no.age.no.ibd.phq.base$na.per.person.phq)
table(dat.no.sex.no.gender.no.age.no.ibd.phq.base$na.per.person.phq)

PHQ.cc$miss_pc_total.phq <- PHQ.cc$na.per.person.phq/PHQ.n.items
freq(PHQ.cc$miss_pc_total.phq)
```

```{r Exclusion of participants because of missing questionnaire items}
dim(dat.no.sex.no.age.no.ibd)
dat.no.sex.no.age.no.ibd.incomplete.phq.questionnaire <- dat.no.sex.no.gender.no.age.no.ibd %>%
  filter(!is.na(phq.items_prepan))

dim(dat.no.sex.no.age.no.ibd.incomplete.questionnaire)

dim(dat.no.sex.no.age.no.ibd)[1]-dim(dat.no.sex.no.age.no.ibd.incomplete.questionnaire)[1]

@@

skimr::skim(dat.glad)
```

The complete rate for sex, gender and age should be 1 now.
